Late Pleistocene stone artefact technology at Mau A, Yen Bai, Norther Vietnam

### 2022-03-04 analysis/paper/paper.Rmd
Reduced axes text size on contribution plots

## Methods

![This is a test.](./test_graphic.png)

@@

plot_grid(

PC1_contrib +
  scale_x_discrete(labels = 
  as.factor(c("X Value: Top Left",
              "Y Value: Top Left",
              "X Value: Mid-Upper Left",
              "Y Value: Mid-Upper Left",
              "X Value: Mid-Lower Left",
              "Y Value: Mid-Lower Left",
              "X Value: Bottom Left",
              "Y Value: Bottom Left",
              "X Value: Distal Tip",
              "Y Value: Distal Tip",
              "X Value: Bottom Right",
              "Y Value: Bottom Right",
              "X Value: Mid-Lower Right",
              "Y Value: Mid-Lower Right",
              "X Value: Mid-Upper Right",
              "Y Value: Mid-Upper Right",
              "X Value: Top Right",
              "Y Value: Top Right"))),
          PC2_contrib + 
    scale_x_discrete(labels = 
  as.factor(c("X Value: Top Left",
              "Y Value: Top Left",
              "X Value: Mid-Upper Left",
              "Y Value: Mid-Upper Left",
              "X Value: Mid-Lower Left",
              "Y Value: Mid-Lower Left",
              "X Value: Bottom Left",
              "Y Value: Bottom Left",
              "X Value: Distal Tip",
              "Y Value: Distal Tip",
              "X Value: Bottom Right",
              "Y Value: Bottom Right",
              "X Value: Mid-Lower Right",
              "Y Value: Mid-Lower Right",
              "X Value: Mid-Upper Right",
              "Y Value: Mid-Upper Right",
              "X Value: Top Right",
              "Y Value: Top Right")))
  )
```

@@

Looking at \@ref(fig:contribution-plots),

>>>>

<!-- QH: Trying to think of a way to make this figure work with the current figure numbering system we have in bookdown. Adding in a number that starts before 1.1 for now -->
## Methods

![Figure 1.0. Schematic figure showing both the intial measurements that were used to generate our landmarks and the location of our landmarks on a hypothetical flake. A, B, C, D, and E are the top horizontal measurement, width at a quarter of the maximum length, maximum dimension length, width at a quarter of the maximum length, and width at three quarter of the maximum length respectively. Points 1 through 9 are all of the landmarks generated from measurements A through E.  ](./test_graphic.png)

@@

plot_grid(PC1_contrib +
          scale_x_discrete(labels = 
                           as.factor(c("X Value: Top Left",
                          "Y Value: Top Left",
                          "X Value: Mid-Upper Left",
                          "Y Value: Mid-Upper Left",
                          "X Value: Mid-Lower Left",
                          "Y Value: Mid-Lower Left",
                          "X Value: Bottom Left",
                          "Y Value: Bottom Left",
                          "X Value: Distal Tip",
                          "Y Value: Distal Tip",
                          "X Value: Bottom Right",
                          "Y Value: Bottom Right",
                          "X Value: Mid-Lower Right",
                          "Y Value: Mid-Lower Right",
                          "X Value: Mid-Upper Right",
                          "Y Value: Mid-Upper Right",
                          "X Value: Top Right",
                          "Y Value: Top Right")))+
             theme(axis.text = element_text(size = 5)),
          PC2_contrib + 
          scale_x_discrete(labels = 
                           as.factor(c("X Value: Top Left",
                           "Y Value: Top Left",
                           "X Value: Mid-Upper Left",
                           "Y Value: Mid-Upper Left",
                           "X Value: Mid-Lower Left",
                           "Y Value: Mid-Lower Left",
                           "X Value: Bottom Left",
                           "Y Value: Bottom Left",
                           "X Value: Distal Tip",
                           "Y Value: Distal Tip",
                           "X Value: Bottom Right",
                           "Y Value: Bottom Right",
                           "X Value: Mid-Lower Right",
                           "Y Value: Mid-Lower Right",
                           "X Value: Mid-Upper Right",
                           "Y Value: Mid-Upper Right",
                           "X Value: Top Right",
                           "Y Value: Top Right")))+
             theme(axis.text = element_text(size = 5))
  )

@@

Looking at \@ref(fig:contribution-plots), one can see that
